Control Script for SCOPE data

### 2022-10-14 metadata/metadata_control.Rmd
Adding MAAs to known compounds and untagging acetyllysine

          mz=289.1393, ionization_form="[M+H]", charge=1) %>%

@@

        mz=333.1292, ionization_form="[M+H]", charge=1) %>%

@@

        mz=245.1132, ionization_form="[M+H]", charge=1) %>%

@@

        mz=347.1449, ionization_form="[M+H]", charge=1) %>%

@@

        mz=303.1186, ionization_form="[M+H]", charge=1) %>%

@@

        mz=285.1445, ionization_form="[M+H]", charge=1) %>%

@@

        mz=246.0972, ionization_form="[M+H]", charge=1) %>%

@@

## Culture data ----

>>>>

          mz=289.1393, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=333.1292, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=245.1132, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=347.1449, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=303.1186, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=285.1445, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

        mz=246.0972, ionization_form="[M+H]", charge=1, polarity="pos") %>%

@@

## Culture data

### 2022-10-14 untargeted/output_control.Rmd
Adding MAAs to known compounds and untagging acetyllysine

polarity <- "neg"
cruise <- "MC"
output_folder <- paste0(c(cruise, polarity, "output/"), collapse = "_")
mzml_path <- paste0("../mzMLs/", polarity, "/")

@@

```{r targeted, purl=TRUE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
given_stans <- read.csv("../metadata/made_data/clean_stans.csv") %>% 
  filter(polarity==!!polarity) %>%
  filter(run_date[1]>=date_added)

>>>>

polarity <- "pos"
cruise <- "MT"
output_folder <- paste0(c(cruise, polarity, "output/"), collapse = "_")
mzml_path <- paste0("../mzMLs/", polarity, "/")

@@

```{r targeted, purl=TRUE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
given_stans <- read.csv("../metadata/made_data/clean_stans.csv") %>% 
  filter(polarity==!!polarity) %>% 
  filter(run_date[1]>=date_added | is.na(date_added))
